\bf The forestecology R package for fitting and assessing neighborhood models of the effect of interspecific competition on the growth of trees

### 2021-07-21 paper/paper.Rmd
tweak
Trying out multiple competitive distances. Wrote code but have not yet run it

Our model of interspecific competition relies on a spatial definition of who competitor trees are: all trees within a distance `comp_dist` of a focal tree. We set `comp_dist` to 7.5m, a value informed by other studies [@canham_neighborhood_2004, @uriarte_spatially_2004, @canham_neighborhood_2006]. We use `comp_dist` and a manually constructed `sf` representation of the study region's boundary as inputs to `add_buffer_variable()` to add a `buffer` boolean variable to `growth_scbi`. All trees with `buffer` equal to `FALSE` will be our focal trees whose growth will be modeled, whereas those with `TRUE` will only act as competitor trees.

@@

We also hope to extend the `forestecology` package's functionality to account for a larger variety of models for tree growth. One clear future direction would be to allow competition based on species trait values rather than species identity. There is evidence that traits predict competitive outcomes [@kunstler_competitive_2012, @lasky_trait-mediated_2014, @uriarte_trait_2010]. Thus an extenstion of the model would allow $lambda$ values to be a function of the traits of competing species.

@@

# Appendix

@@

```{r appendix-code, eval = FALSE, cache = FALSE}
library(tidyverse)
library(lubridate)
library(here)
library(sf)
library(viridis)
library(forestecology)
library(blockCV)
library(tictoc)

@@

>>>>

Our model of interspecific competition relies on a spatial definition of who competitor trees are: all trees within a distance `comp_dist` of a focal tree. Here we set `comp_dist` to 7.5m, a value informed by other studies [@canham_neighborhood_2004, @uriarte_spatially_2004, @canham_neighborhood_2006], but the package could also be used to compare multiple distances and see which is best supported (see Appendix 2 \ref{mult-dist}). We use `comp_dist` and a manually constructed `sf` representation of the study region's boundary as inputs to `add_buffer_variable()` to add a `buffer` boolean variable to `growth_scbi`. All trees with `buffer` equal to `FALSE` will be our focal trees whose growth will be modeled, whereas those with `TRUE` will only act as competitor trees.

@@

We also hope to extend the `forestecology` package's functionality to account for a larger variety of models for tree growth. One clear future direction would be to allow competition based on species trait values rather than species identity. There is evidence that traits predict competitive outcomes [@kunstler_competitive_2012, @lasky_trait-mediated_2014, @uriarte_trait_2010]. Thus an extension of the model would allow $\lambda$ values from Equation \ref{eq:model} to be a function of the traits of competing species.

@@

# Appendix 1: Replicate RMSE comparison

@@

```{r appendix1-code, eval = FALSE, cache = FALSE}
library(tidyverse)
library(lubridate)
library(here)
library(sf)
library(viridis)
library(forestecology)
library(blockCV)
library(tictoc)

@@

# Appendix 2: Compare different competitive distances {#mult-dist}

Above we set the cut off distance for two stems to compete at 7.5 m. Our package can be used to find which distance is best supported by the data. Here we give an example.

```{r appendix2-code}

mult_dist_comp <- tibble(
  dist = c(2.5, 5, 7.5, 10, 12.5 ),
  rmse = 0
)

for (i in 1:length(mult_dist_comp$dist))
{
  comp_dist <- mult_dist_comp$dist[i]
  growth_scbi <- growth_scbi %>%
    add_buffer_variable(size = comp_dist, region = study_region_scbi)

  focal_vs_comp_scbi <- growth_scbi %>%
    create_focal_vs_comp(comp_dist, blocks = blocks_scbi, id = "stemID")
  focal_vs_comp_scbi %>% 
    select(focal_ID, focal_sp, geometry, growth, comp)

  focal_vs_comp_scbi <- focal_vs_comp_scbi %>%
    run_cv(comp_dist = mult_dists[i], blocks = blocks_scbi)

  mult_dist_comp$rmse[i] <- focal_vs_comp_scbi %>%
    rmse(truth = growth, estimate = growth_hat) %>%
    pull(.estimate)
}

mult_dist_comp %>%
  ggplot(aes(dist,rmse)) +
  geom_point() +
  xlab('Distance (m)') +
  ylab('RMSE (cm)')

```

### 2021-07-21 paper/paper.tex
Trying out multiple competitive distances. Wrote code but have not yet run it

Our model of interspecific competition relies on a spatial definition of
who competitor trees are: all trees within a distance
\texttt{comp\_dist} of a focal tree. We set \texttt{comp\_dist} to 7.5m,
a value informed by other studies \citep[\citet{uriarte_spatially_2004},
\citet{canham_neighborhood_2006}]{canham_neighborhood_2004}. We use
\texttt{comp\_dist} and a manually constructed \texttt{sf}
representation of the study region's boundary as inputs to
\texttt{add\_buffer\_variable()} to add a \texttt{buffer} boolean
variable to \texttt{growth\_scbi}. All trees with \texttt{buffer} equal
to \texttt{FALSE} will be our focal trees whose growth will be modeled,
whereas those with \texttt{TRUE} will only act as competitor trees.

@@

>>>>

Our model of interspecific competition relies on a spatial definition of
who competitor trees are: all trees within a distance
\texttt{comp\_dist} of a focal tree. Here we set \texttt{comp\_dist} to
7.5m, a value informed by other studies
\citep[\citet{uriarte_spatially_2004},
\citet{canham_neighborhood_2006}]{canham_neighborhood_2004}, but the
package could also be used to compare multiple distances and see which
is best supported (see Appendix 2 \ref{mult-dist}). We use
\texttt{comp\_dist} and a manually constructed \texttt{sf}
representation of the study region's boundary as inputs to
\texttt{add\_buffer\_variable()} to add a \texttt{buffer} boolean
variable to \texttt{growth\_scbi}. All trees with \texttt{buffer} equal
to \texttt{FALSE} will be our focal trees whose growth will be modeled,
whereas those with \texttt{TRUE} will only act as competitor trees.

@@

\hypertarget{appendix-1-replicate-rmse-comparison}{%
\section{Appendix 1: Replicate RMSE
comparison}\label{appendix-1-replicate-rmse-comparison}}

This code replicates Figure \ref{fig:scbi-simulation}: A comparison of
root mean squared error of models for standard, permuted, and spatial
cross- validated error estimates.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(tidyverse)}
\KeywordTok{library}\NormalTok{(lubridate)}
\KeywordTok{library}\NormalTok{(here)}
\KeywordTok{library}\NormalTok{(sf)}
\KeywordTok{library}\NormalTok{(viridis)}
\KeywordTok{library}\NormalTok{(forestecology)}
\KeywordTok{library}\NormalTok{(blockCV)}
\KeywordTok{library}\NormalTok{(tictoc)}

\CommentTok{# Compute growth of trees based on census data -------------------------}
\NormalTok{census_}\DecValTok{2013}\NormalTok{_scbi <-}\StringTok{ }\KeywordTok{here}\NormalTok{(}\StringTok{"paper/scbi.stem2.csv"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{read_csv}\NormalTok{() }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{select}\NormalTok{(stemID, sp, }\DataTypeTok{date =}\NormalTok{ ExactDate, gx, gy, dbh, codes, status) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}
    \DataTypeTok{date =} \KeywordTok{mdy}\NormalTok{(date),}
    \DataTypeTok{dbh =} \KeywordTok{as.numeric}\NormalTok{(dbh)}\OperatorTok{/}\DecValTok{10}
\NormalTok{  ) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(gx }\OperatorTok{<}\StringTok{ }\DecValTok{300}\NormalTok{, }\KeywordTok{between}\NormalTok{(gy, }\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{))}

\NormalTok{census_}\DecValTok{2018}\NormalTok{_scbi <-}\StringTok{ }\KeywordTok{here}\NormalTok{(}\StringTok{"paper/scbi.stem3.csv"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{read_csv}\NormalTok{() }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{select}\NormalTok{(stemID, sp, }\DataTypeTok{date =}\NormalTok{ ExactDate, gx, gy, dbh, codes, status) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}
    \DataTypeTok{date =} \KeywordTok{mdy}\NormalTok{(date),}
    \DataTypeTok{dbh =} \KeywordTok{as.numeric}\NormalTok{(dbh)}\OperatorTok{/}\DecValTok{10}
\NormalTok{  ) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(gx }\OperatorTok{<}\StringTok{ }\DecValTok{300}\NormalTok{, }\KeywordTok{between}\NormalTok{(gy, }\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{))}

\NormalTok{growth_scbi <-}
\StringTok{  }\KeywordTok{compute_growth}\NormalTok{(}
    \DataTypeTok{census_1 =}\NormalTok{ census_}\DecValTok{2013}\NormalTok{_scbi,}
    \DataTypeTok{census_2 =}\NormalTok{ census_}\DecValTok{2018}\NormalTok{_scbi }\OperatorTok{%>%}\StringTok{ }\KeywordTok{filter}\NormalTok{(}\OperatorTok{!}\KeywordTok{str_detect}\NormalTok{(codes, }\StringTok{"R"}\NormalTok{)),}
    \DataTypeTok{id =} \StringTok{"stemID"}
\NormalTok{  )}

\CommentTok{# Add spatial information ----------------------------------------------}
\CommentTok{# Define buffer region using competitive distance range}
\NormalTok{comp_dist <-}\StringTok{ }\FloatTok{7.5}

\NormalTok{study_region_scbi <-}\StringTok{ }\KeywordTok{tibble}\NormalTok{(}
  \DataTypeTok{x =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{0}\NormalTok{, }\DecValTok{0}\NormalTok{),}
  \DataTypeTok{y =} \KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{, }\DecValTok{600}\NormalTok{, }\DecValTok{300}\NormalTok{)}
\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{sf_polygon}\NormalTok{()}

\NormalTok{growth_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{add_buffer_variable}\NormalTok{(}\DataTypeTok{size =}\NormalTok{ comp_dist, }\DataTypeTok{region =}\NormalTok{ study_region_scbi)}

\CommentTok{# Manually define spatial blocks to act as folds}
\NormalTok{fold1 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{300}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{300}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{450}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{450}\NormalTok{))}
\NormalTok{fold2 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{300}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{450}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{450}\NormalTok{))}
\NormalTok{fold3 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{450}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{450}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{600}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{600}\NormalTok{))}
\NormalTok{fold4 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{450}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{450}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{600}\NormalTok{))}
\NormalTok{n_fold <-}\StringTok{ }\DecValTok{4}

\NormalTok{blocks_scbi <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(}
  \KeywordTok{sf_polygon}\NormalTok{(fold1), }\KeywordTok{sf_polygon}\NormalTok{(fold2), }
  \KeywordTok{sf_polygon}\NormalTok{(fold3), }\KeywordTok{sf_polygon}\NormalTok{(fold4)}
\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{folds =} \KeywordTok{c}\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{n_fold) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{factor}\NormalTok{())}

\CommentTok{# Associate each observation to a fold}
\NormalTok{SpatialBlock_scbi <-}\StringTok{ }\KeywordTok{spatialBlock}\NormalTok{(}
  \DataTypeTok{speciesData =}\NormalTok{ growth_scbi, }\DataTypeTok{k =}\NormalTok{ n_fold, }\DataTypeTok{selection =} \StringTok{"systematic"}\NormalTok{,}
  \DataTypeTok{blocks =}\NormalTok{ blocks_scbi, }\DataTypeTok{showBlocks =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{verbose =} \OtherTok{FALSE}
\NormalTok{)}

\NormalTok{growth_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{foldID =}\NormalTok{ SpatialBlock_scbi}\OperatorTok{$}\NormalTok{foldID }\OperatorTok{%>%}\StringTok{ }\KeywordTok{factor}\NormalTok{())}

\CommentTok{# Compute focal versus competitor tree information ---------------------}
\NormalTok{focal_vs_comp_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{create_focal_vs_comp}\NormalTok{(comp_dist, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi, }\DataTypeTok{id =} \StringTok{"stemID"}\NormalTok{)}

\CommentTok{# Fit model and make predictions ---------------------------------------}
\CommentTok{# Number of permutation shuffles:}
\NormalTok{num_shuffle <-}\StringTok{ }\DecValTok{49}

\CommentTok{# Save results here}
\NormalTok{run_time <-}\StringTok{ }\DecValTok{0}
\NormalTok{observed_RMSE <-}\StringTok{ }\DecValTok{0}
\NormalTok{observed_RMSE_CV <-}\StringTok{ }\DecValTok{0}
\NormalTok{shuffle_RMSE <-}\StringTok{ }\KeywordTok{vector}\NormalTok{(}\StringTok{"list"}\NormalTok{, }\DecValTok{1}\NormalTok{)}
\NormalTok{shuffle_RMSE_CV <-}\StringTok{ }\KeywordTok{vector}\NormalTok{(}\StringTok{"list"}\NormalTok{, }\DecValTok{1}\NormalTok{)}
\NormalTok{filename <-}\StringTok{ }\KeywordTok{here}\NormalTok{(}\StringTok{"paper/simulation_results/"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{str_c}\NormalTok{(}\StringTok{"2021-03-03_scbi_"}\NormalTok{, num_shuffle, }\StringTok{"_shuffles"}\NormalTok{)}

\CommentTok{# Run all simulations}
\CommentTok{# 0. Setup simulation for this species type ----}
\CommentTok{# Start clock}
\KeywordTok{tic}\NormalTok{()}

\CommentTok{# 1. Compute observed test statistic: RMSE with no cross-validation ----}
\CommentTok{# Fit model (compute posterior parameters)}
\NormalTok{comp_bayes_lm_scbi <-}\StringTok{ }\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{comp_bayes_lm}\NormalTok{(}\DataTypeTok{prior_param =} \OtherTok{NULL}\NormalTok{, }\DataTypeTok{run_shuffle =} \OtherTok{FALSE}\NormalTok{)}

\CommentTok{# Make predictions and compute RMSE}
\NormalTok{observed_RMSE <-}\StringTok{ }\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{growth_hat =} 
           \KeywordTok{predict}\NormalTok{(comp_bayes_lm_scbi, focal_vs_comp_scbi)) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{rmse}\NormalTok{(}\DataTypeTok{truth =}\NormalTok{ growth, }\DataTypeTok{estimate =}\NormalTok{ growth_hat) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{pull}\NormalTok{(.estimate)}

\CommentTok{# 2. Compute observed test statistic: RMSE with cross-validation -------}
\NormalTok{observed_RMSE_CV <-}\StringTok{ }\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{run_cv}\NormalTok{(}\DataTypeTok{comp_dist =}\NormalTok{ comp_dist, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{rmse}\NormalTok{(}\DataTypeTok{truth =}\NormalTok{ growth, }\DataTypeTok{estimate =}\NormalTok{ growth_hat) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{pull}\NormalTok{(.estimate)}

\CommentTok{# 3. Permutation distribution: RMSE with no cross-validation -----------}
\CommentTok{# Compute num_shuffle permutation test statistics}
\NormalTok{shuffle_RMSE <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\DataTypeTok{length =}\NormalTok{ num_shuffle)}
\ControlFlowTok{for}\NormalTok{(j }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\NormalTok{num_shuffle)\{}
  \CommentTok{# Fit model (compute posterior parameters) with shuffling}
\NormalTok{  comp_bayes_lm_scbi <-}\StringTok{ }\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{comp_bayes_lm}\NormalTok{(}\DataTypeTok{prior_param =} \OtherTok{NULL}\NormalTok{, }\DataTypeTok{run_shuffle =} \OtherTok{TRUE}\NormalTok{)}

  \CommentTok{# Make predictions and compute RMSE}
\NormalTok{  shuffle_RMSE[j] <-}\StringTok{  }\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{growth_hat =} 
             \KeywordTok{predict}\NormalTok{(comp_bayes_lm_scbi, focal_vs_comp_scbi)) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{rmse}\NormalTok{(}\DataTypeTok{truth =}\NormalTok{ growth, }\DataTypeTok{estimate =}\NormalTok{ growth_hat) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{pull}\NormalTok{(.estimate)}
\NormalTok{\}}

\CommentTok{# 4. Permutation distribution: RMSE with cross-validation --------------}
\CommentTok{# Compute num_shuffle permutation test statistics}
\NormalTok{shuffle_RMSE_CV <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\DataTypeTok{length =}\NormalTok{ num_shuffle)}

\CommentTok{# Compute num_shuffle permutation test statistics}
\ControlFlowTok{for}\NormalTok{(j }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\NormalTok{num_shuffle)\{}
  \CommentTok{# Compute and save RMSE}
\NormalTok{  shuffle_RMSE_CV[j] <-}\StringTok{ }\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{run_cv}\NormalTok{(}\DataTypeTok{comp_dist =}\NormalTok{ comp_dist, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi, }
           \DataTypeTok{run_shuffle =} \OtherTok{TRUE}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{rmse}\NormalTok{(}\DataTypeTok{truth =}\NormalTok{ growth, }\DataTypeTok{estimate =}\NormalTok{ growth_hat) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{pull}\NormalTok{(.estimate)}

  \CommentTok{# Status update}
  \KeywordTok{str_c}\NormalTok{(}\StringTok{"Shuffle with permutation "}\NormalTok{, j, }\StringTok{" at "}\NormalTok{, }\KeywordTok{Sys.time}\NormalTok{()) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{print}\NormalTok{()}
\NormalTok{\}}

\CommentTok{# 5. Save results ----}
\NormalTok{clock <-}\StringTok{ }\KeywordTok{toc}\NormalTok{(}\DataTypeTok{quiet =} \OtherTok{TRUE}\NormalTok{)}
\NormalTok{run_time <-}\StringTok{ }\NormalTok{clock}\OperatorTok{$}\NormalTok{toc }\OperatorTok{-}\StringTok{ }\NormalTok{clock}\OperatorTok{$}\NormalTok{tic}

\NormalTok{model_comp_tbl <-}\StringTok{ }\KeywordTok{tibble}\NormalTok{(}
  \DataTypeTok{run_time =}\NormalTok{ run_time,}
  \DataTypeTok{observed_RMSE =}\NormalTok{ observed_RMSE,}
  \DataTypeTok{observed_RMSE_CV =}\NormalTok{ observed_RMSE_CV,}
  \DataTypeTok{shuffle_RMSE =}\NormalTok{ shuffle_RMSE,}
  \DataTypeTok{shuffle_RMSE_CV =}\NormalTok{ shuffle_RMSE_CV,}
\NormalTok{)}
\KeywordTok{save}\NormalTok{(model_comp_tbl, }\DataTypeTok{file =}\NormalTok{ filename }\OperatorTok{%>%}\StringTok{ }\KeywordTok{str_c}\NormalTok{(}\StringTok{".RData"}\NormalTok{))}

\CommentTok{# Visualize results ----------------------------------------------------}
\NormalTok{model_comp <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(}
\NormalTok{  model_comp_tbl }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{select}\NormalTok{(run_time, }\DataTypeTok{observed =}\NormalTok{ observed_RMSE, }
           \DataTypeTok{shuffle =}\NormalTok{ shuffle_RMSE) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{CV =} \OtherTok{FALSE}\NormalTok{),}
\NormalTok{  model_comp_tbl }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{select}\NormalTok{(run_time, }\DataTypeTok{observed =}\NormalTok{ observed_RMSE_CV, }
           \DataTypeTok{shuffle =}\NormalTok{ shuffle_RMSE_CV) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{CV =} \OtherTok{TRUE}\NormalTok{)}
\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{gather}\NormalTok{(type, RMSE, }\OperatorTok{-}\KeywordTok{c}\NormalTok{(run_time, CV))}

\NormalTok{model_comp_observed <-}\StringTok{ }\NormalTok{model_comp }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(type }\OperatorTok{==}\StringTok{ "observed"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{unnest}\NormalTok{(}\DataTypeTok{cols =} \KeywordTok{c}\NormalTok{(RMSE))}
\NormalTok{model_comp_shuffle <-}\StringTok{ }\NormalTok{model_comp }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(type }\OperatorTok{==}\StringTok{ "shuffle"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{unnest}\NormalTok{(}\DataTypeTok{cols =} \KeywordTok{c}\NormalTok{(RMSE))}

\NormalTok{cv_plot <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_vline}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ model_comp_observed, }
             \KeywordTok{aes}\NormalTok{(}\DataTypeTok{xintercept =}\NormalTok{ RMSE, }\DataTypeTok{col =}\NormalTok{ CV), }
             \DataTypeTok{linetype =} \StringTok{"dashed"}\NormalTok{, }\DataTypeTok{show.legend =}\NormalTok{ F) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_histogram}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ model_comp_shuffle, }
                 \KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ RMSE, }\DataTypeTok{fill =}\NormalTok{ CV), }\DataTypeTok{bins =} \DecValTok{50}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{labs}\NormalTok{(}
    \DataTypeTok{fill =} \StringTok{"Cross-validated?"}\NormalTok{,}
    \DataTypeTok{x =} \KeywordTok{expression}\NormalTok{(}\KeywordTok{paste}\NormalTok{(}\StringTok{"RMSE (cm "}\NormalTok{, y}\OperatorTok{^}\NormalTok{\{}\OperatorTok{-}\DecValTok{1}\NormalTok{\}, }\StringTok{")"}\NormalTok{))}
\NormalTok{  ) }\OperatorTok{+}
\StringTok{  }\KeywordTok{scale_color_viridis}\NormalTok{(}\DataTypeTok{discrete =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{option =} \StringTok{"D"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{scale_fill_viridis}\NormalTok{(}\DataTypeTok{discrete =} \OtherTok{TRUE}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme_light}\NormalTok{()}
\NormalTok{cv_plot}

\NormalTok{filename }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{str_c}\NormalTok{(}\StringTok{".pdf"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{ggsave}\NormalTok{(}\DataTypeTok{plot =}\NormalTok{ cv_plot, }\DataTypeTok{width =} \DecValTok{16}\OperatorTok{/}\DecValTok{2}\NormalTok{, }\DataTypeTok{height =} \DecValTok{9}\OperatorTok{/}\DecValTok{2}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\hypertarget{mult-dist}{%
\section{Appendix 2: Compare different competitive
distances}\label{mult-dist}}
